\textbf{Computational Fuzzy Extractors}

### 2013-02-15 trunk/CompFuzzExt.tex
Initial commit

We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).  We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
\begin{lemma}
\label{lem:conversion to unpredictability}
Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon, s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
for $s_{sec}'\approx s_{sec}$.
\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.  We provide a formal description of our algorithm in the next section.
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.

>>>>

We will restate any $\distLWE_{n, m, q, \chi}$ formulation using unpredictability entropy~(recall \defref{def:unp entropy}).  We have the following statement about the unpredictability of $\LWE$ problems~(proof in \secref{sec:proof of unpred conversion}).
\begin{lemma}
\label{lem:conversion to unpredictability}
Assume that $\distLWE_{n-k, m, q, \chi}$ is $(\epsilon, s_{sec})$-hard and $m\geq n$ then  $H^{\unp}_{\epsilon', s_{sec}'}(E|\vA, \vA X+E) \geq k\log q$
for $\epsilon' \approx \epsilon, s_{sec}'\approx s_{sec}$.
\end{lemma}
%\begin{lemma}
%\label{lem:dmq with unp entropy}
%Let $n$ be a security parameter.  Let $q = q(n) = \poly(n)$ be a prime integer and $m = m(n) = \poly(n)$ be an integer. Let $\gamma\in (0, 1)$ be a constant and let $\rho\in (0,1)$ such that $\rho q \geq 2n^{1/2+3\gamma}m$.  Assume that approximating GAPSVP and SIVP using a polynomial time quantum algorithm is hard within a factor of $\tilde{O}(n^{1/2+3\gamma}m/\rho)$.  Let $\vA\in \Fq^{m\times n}, X\in\Fq^{n}, E\in [-\rho q, \rho q]^m$ be drawn uniformly.  Then for $s_{sec} = \poly(n)$ and $\epsilon = \ngl(n)$
%\[
%H^{\unp}_{\epsilon, s_{sec}}(E| AX+E) = \min\{|X|, |E|\} = \min \{ n\log q, m\log \rho q\}
%\]
%\end{lemma}
With \lemref{lem:uniform LWE decision} we can use the code-offset construction in \consref{cons:informal construction} and retain unpredictability entropy $n\log q$.  We provide a formal description of our algorithm in the next section.
%\lemref{lem:uniform LWE decision} has two advantages: 1) We can use the code-offset construction from \consref{cons:informal construction}. 2) The error term is distributed over a smaller interval $[-\rho q, \rho q]$ instead of $\Fq$.
